{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-17 paper/paper.tex
added intuition of the next function

\subsection{Instantiation}
\label{sec:instantiation}

>>>>

An important hypothesis to succeed in the proof of this theorem is the existence
of a \texttt{next} function. This \texttt{next} function should compute for every
high program point the first subsequent program point with a low security level. With
this function one is able to detect when a hidden thread is allowed to become visible
again.
\subsection{Instantiation}
\label{sec:instantiation}
